---
title: "Descriptives"
author: "Julie Driebe & Ruben Arslan"
date: "20 12 2020"
output: html_document
---

# Fertility and Kin - Descriptives {.tabset}
```{r}
knitr::opts_chunk$set(warning =  F, message = F)
```

## load and prepare data {.tabset}
```{r}
source("0_helpers.R")
library(effsize)
library(tidyverse)

all_surveys <- readRDS("persons.rds")
diary <- readRDS("diary_persons.rds")

## only participants fullfilling inclusion criteria and not living with parents 
all_surveys_included = all_surveys %>% filter(reasons_for_exclusion == "" & abode_flat_share  != 2)
hc = all_surveys_included %>% filter(hormonal_contraception == T)
nc = all_surveys_included %>% filter(hormonal_contraception == F)
```

## descriptives {.tabset}

### distribution {.tabset}
```{r}
## nc vs hc
xtabs(~ hormonal_contraception, all_surveys_included)

## single vs relationship
xtabs(~ relationship_status == 1, all_surveys_included)

## relationship status + contraception
xtabs(~ (relationship_status == 1) + hormonal_contraception, all_surveys_included)

## percentage hc vs nc
round(prop.table(xtabs(~ hormonal_contraception, all_surveys_included))*100 ,2)
```

### NC {.tabset}
```{r}
all_surveys_included %>% filter(hormonal_contraception == F) %>% select(age, religiosity, first_time, menstruation_length, number_sexual_partner, menarche, bfi_agree, bfi_open, bfi_neuro, bfi_extra, bfi_consc) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame()

```


### HC {.tabset}
```{r}
all_surveys_included %>% filter(hormonal_contraception == T) %>% select(age, religiosity, first_time, menstruation_length, number_sexual_partner, menarche, bfi_agree, bfi_open, bfi_neuro, bfi_extra, bfi_consc) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  dplyr::summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame()
```
### single women {.tabset}

#### NC {.tabset}
```{r}
all_surveys_included %>% filter(hormonal_contraception == F & relationship_status == 1) %>% select(age, religiosity, first_time, menstruation_length, number_sexual_partner, menarche, bfi_agree, bfi_open, bfi_neuro, bfi_extra, bfi_consc) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  dplyr::summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame()

```

#### HC {.tabset}
```{r}
all_surveys_included %>% filter(hormonal_contraception == T & relationship_status == 1) %>% select(age, religiosity, first_time, menstruation_length, number_sexual_partner, menarche, bfi_agree, bfi_open, bfi_neuro, bfi_extra, bfi_consc) %>%
  gather(variable, value) %>%
  group_by(variable) %>%
  filter(!is.na(value)) %>%
  dplyr::summarise(mean = mean(value), sd = sd(value), 
            median = median(value),
            min = min(value), max  = max(value)) %>%
  data.frame()

```

## compare groups {.tabset}

### age {.tabset}
```{r}
t.test(hc$age, nc$age)
cohen.d(hc$age, nc$age, hedges.correction = T, pooled = F)
```

### religiosity {.tabset}
```{r}
t.test(hc$religiosity, nc$religiosity)
cohen.d(hc$religiosity, nc$religiosity, hedges.correction = T, pooled = F)
```

### first time {.tabset}
```{r}
t.test(hc$first_time, nc$first_time)
cohen.d(hc$first_time, nc$first_time, hedges.correction = T, pooled = F, na.rm =T)
```

### menarche {.tabset}
```{r}
t.test(hc$menarche, nc$menarche)
cohen.d(hc$menarche, nc$menarche, hedges.correction = T, pooled = F)
```

### cycle length {.tabset}
```{r}
t.test(hc$menstruation_length, nc$menstruation_length)
cohen.d(hc$menstruation_length, nc$menstruation_length, hedges.correction = T, pooled = F)
```

### nr sex partner {.tabset}
```{r}
t.test(hc$number_sexual_partner, nc$number_sexual_partner)
cohen.d(hc$number_sexual_partner, nc$number_sexual_partner, hedges.correction = T, pooled = F)
```

### extraversion {.tabset}
```{r}
t.test(hc$bfi_extra, nc$bfi_extra)
cohen.d(hc$bfi_extra, nc$bfi_extra, hedges.correction = T, pooled = F)
```

### agreeableness {.tabset}
```{r}
t.test(hc$bfi_agree, nc$bfi_agree)
cohen.d(hc$bfi_agree, nc$bfi_agree, hedges.correction = T, pooled = F)
```

### neuroticism {.tabset}
```{r}
t.test(hc$bfi_neuro, nc$bfi_neuro)
cohen.d(hc$bfi_neuro, nc$bfi_neuro, hedges.correction = T, pooled = F)
```

### conscientiousness {.tabset}
```{r}
t.test(hc$bfi_consc, nc$bfi_consc)
cohen.d(hc$bfi_consc, nc$bfi_consc, hedges.correction = T, pooled = F)
```

### openness {.tabset}
```{r}
t.test(hc$bfi_open, nc$bfi_open)
cohen.d(hc$bfi_open, nc$bfi_open, hedges.correction = T, pooled = F)
```


## Time spent with whom
```{r}
diary %>% filter(reasons_for_exclusion == "") %>% 
  select(time_family, person_is_related_man, person_is_related_woman) %>% cor(use = 'p') %>% round(2)

diary %>% filter(reasons_for_exclusion == "") %>% 
  xtabs(~ time_family + I(person_is_related_man>0) + I(person_is_related_woman>0), .)
```

## Exclusion reasons

### Between subjects
```{r}
exclusion_reasons <- all_surveys %>% 
  mutate(reasons_for_exclusion = str_sub(reasons_for_exclusion, 1, -3)) %>% 
  select(session, reasons_for_exclusion) %>% 
  drop_na(session) %>% 
  comma_separated_to_columns(reasons_for_exclusion)

exclusion_reasons_table <- exclusion_reasons %>% 
  select(-session) %>% 
  summarise_all(sum) %>% 
  sort() %>% 
  gather(reason, n) %>% 
  left_join(diary %>% mutate(reason = str_sub(reasons_for_exclusion, 1, -3)) %>% group_by(reason) %>% summarise(unique = n())) %>% 
  mutate(unique = if_else(is.na(unique), 0L, unique)) %>% 
  left_join(exclusion_reasons %>% 
  gather(reason, n, -session) %>% 
  filter(n > 0) %>% 
  distinct(session, reason, n) %>% 
  group_by(reason) %>%
  summarise(n_women = sum(n)))

library(UpSetR)
exclusion_reasons %>% 
  filter(included == 0) %>% 
  select(-included) %>% 
  as.data.frame() %>% 
  {
  upset(., ncol(.), 20, show.numbers = TRUE, order.by = "freq",
      main.bar.color = "#6E8691",
      matrix.color = "#6E8691",
      sets.bar.color = "#53AC9B")
  }

exclusion_reasons_table %>% 
  knitr::kable(caption = "Reasons for exclusion. _n_ shows the number of affected women, _unique_ those who for whom this was the only reason to be excluded.")
```


### Diary
```{r}
exclusion_reasons_diary <- diary %>% 
  mutate(reasons_for_exclusion = str_sub(reasons_for_exclusion, 1, -3)) %>% 
  select(session, created_date, reasons_for_exclusion) %>% 
  drop_na(session, created_date) %>% 
  comma_separated_to_columns(reasons_for_exclusion) %>% 
  select( -created_date)

exclusion_reasons_diary_table <- exclusion_reasons_diary %>% 
  select(-session) %>% 
  summarise_all(sum) %>% 
  sort() %>% 
  gather(reason, n) %>% 
  left_join(diary %>% mutate(reason = str_sub(reasons_for_exclusion, 1, -3)) %>% group_by(reason) %>% summarise(unique = n())) %>% 
  mutate(unique = if_else(is.na(unique), 0L, unique)) %>% 
  left_join(exclusion_reasons_diary %>% 
  gather(reason, n, -session) %>% 
  filter(n > 0) %>% 
  distinct(session, reason, n) %>% 
  group_by(reason) %>%
  summarise(n_women = sum(n)))

library(UpSetR)
exclusion_reasons_diary %>% 
  filter(included == 0) %>% 
  select(-included) %>% 
  as.data.frame() %>% 
  {
  upset(., ncol(.), 20, show.numbers = TRUE, order.by = "freq",
      main.bar.color = "#6E8691",
      matrix.color = "#6E8691",
      sets.bar.color = "#53AC9B")
  }

exclusion_reasons_diary_table %>% 
  knitr::kable(caption = "Reasons for exclusion. _n_ shows the number of affected women, _unique_ those who for whom this was the only reason to be excluded.")
```
