---
title: "_robustness_model"
date: "21 November 2018"
output: html_document
---

### Robustness checks {.tabset}

#### Basic model

```{r}
library(effects); library(lme4); library(lmerTest); library(knitr); library(brms)

summary(model)
outcome <- model$formula[[1]][[2]]
```

#### Full random slopes

```{r}
add_mod_formula = update.formula(
    formula(model),
    new = as.formula(. ~ . - (1 + fertile_fab | person) + (1 + premenstrual_phase_fab + menstruation + fertile_fab | person ))) # reorder so that the triptych looks nice

 full_random_slopes = update(model, recompile = TRUE, iter = 6000, warmup = 4000, cores = 4, formula = add_mod_formula, newdata = diary %>% filter(reasons_for_exclusion == ""), file= paste0("brms_fits/", model_prefix, "rob_check_full_random_slopes"))

summary(full_random_slopes)
```


#### Full random slopes, no correlations

```{r}
add_mod_formula = update.formula(
    formula(model),
    new = as.formula(. ~ . - (1 + fertile_fab | person) + (1 + premenstrual_phase_fab + menstruation + fertile_fab || person ))) # reorder so that the triptych looks nice

 full_random_slopes_no_cor = update(model, recompile = TRUE, iter = 6000, warmup = 4000, cores = 4, formula = add_mod_formula, newdata = diary %>% filter(reasons_for_exclusion == ""), file= paste0("brms_fits/", model_prefix, "rob_check_full_random_slopes_no_cor"))

summary(full_random_slopes_no_cor)
```

#### Without random slopes

```{r}
no_varying_slope = update(model, recompile = TRUE, formula = . ~ . - (1 + fertile_fab | person) + (1|person), cores = 4, file = paste0("brms_fits/", model_prefix, "rob_check_no_varying_slope"))

summary(no_varying_slope)
```

#### Only women with outcome variability

```{r}
with_outcome_var = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% group_by(session) %>% filter(sd(!!outcome, na.rm = T) > 0), file = paste0("brms_fits/", model_prefix, "rob_check_with_outcome_var"))

summary(with_outcome_var)
```

#### Ordinal model

```{r}
if(identical(model$family$family, "gaussian")) {
  ordinal_model = update(model, recompile = TRUE, family = cumulative(), newdata = diary %>% mutate(time_family = as.integer(1 + time_family)) %>% filter(reasons_for_exclusion == ""), file= paste0("brms_fits/", model_prefix, "rob_check_full_ordinal_model"))
  summary(ordinal_model)
} 
```

#### Gaussian model
```{r}
if(identical(model$family$family, "poisson")) {
  gaussian_model = update(model, recompile = TRUE, family = gaussian(), file= paste0("brms_fits/", model_prefix, "rob_check_full_ordinal_model"))
  summary(gaussian_model)
}
```

#### No exclusions

```{r}
no_exclusions = update(model, recompile = TRUE, cores = 4, newdata = diary, file=paste0("brms_fits/", model_prefix, "rob_check_no_exclusions"))

summary(no_exclusions)
```

#### Exclude cycles shorter than 25 days

```{r}
rob_check_mens_length = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(cycle_length >= 25), file=paste0("brms_fits/", model_prefix, "rob_check_mens_length"))

summary(rob_check_mens_length)
```

#### Exclude women who report cycles outside 25-35

```{r}
rob_check_selfrepcycle_length = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(menstruation_length >= 25, menstruation_length <= 35), file=paste0("brms_fits/", model_prefix, "rob_check_selfrepcycle_length"))

summary(rob_check_selfrepcycle_length)
```


#### Exclude women who report cycles varying more than 1-2 days

```{r}
rob_check_menstruation_regularity = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(menstruation_regularity <= 2), file=paste0("brms_fits/", model_prefix, "rob_check_menstruation_regularity"))

summary(rob_check_menstruation_regularity)
```


#### Exclude women who report uncertainty larger than ±2 days
Across three items (last menstrual onset, cycle length, menstruation regularity).

```{r}
diary$menstruation_certainty <- rowMeans(diary %>% select(menstruation_last_certainty, menstruation_regularity_certainty, menstruation_length_certainty), na.rm = T)
rob_check_menstruation_certainty = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(menstruation_certainty <= 3), file=paste0("brms_fits/", model_prefix, "rob_check_menstruation_certainty"))

summary(rob_check_menstruation_certainty)
```

#### Exclude women who report not feeling healthy

```{r}
rob_check_health = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(self_rated_health <= 2), file=paste0("brms_fits/", model_prefix, "rob_check_health"))

summary(rob_check_health)
```

#### Exclude women trying for pregnancy

```{r}
pregnant_trying = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(pregnant_trying < 4), file=paste0("brms_fits/", model_prefix, "rob_check_pregnant_trying"))

summary(pregnant_trying)
```


#### Include women living with parents
```{r}
rob_check_parents = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "" | reasons_for_exclusion == "living_with_parents, "), file=paste0("brms_fits/", model_prefix, "rob_check_parents"))

summary(rob_check_parents)
```

#### Exclude non-singles

```{r}
if(outcome != "person_is_related_man_seen") {
  rob_check_singles = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "", hetero_relationship == 0, relationship_status == 1), file=paste0("brms_fits/", model_prefix, "rob_check_singles"))

summary(rob_check_singles)
}
```

#### Moderation by weekend

```{r}
weekend = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(weekend == 1), file=paste0("brms_fits/", model_prefix, "rob_check_weekend"))
weekday = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(weekend == 0), file=paste0("brms_fits/", model_prefix, "rob_check_weekday"))

summary(weekend)
summary(weekday)
```

#### Moderation by age group

```{r}
older25 = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(age > 25), file=paste0("brms_fits/", model_prefix, "rob_check_older25"))
younger25 = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(age <= 25), file=paste0("brms_fits/", model_prefix, "rob_check_younger25"))

summary(younger25)
summary(older25)
```

#### Excluding women who used psychopharmacological, hormonal, or antibiotic medication

```{r}
diary <- diary %>% filter(reasons_for_exclusion == "") %>% ungroup() %>% 
  mutate(medication_psychopharmacological = if_else(is.na(medication_psychopharmacological), 0, medication_psychopharmacological),
         medication_hormonal = if_else(is.na(medication_hormonal), 0, medication_hormonal),
         medication_antibiotics = if_else(is.na(medication_antibiotics), 0, medication_antibiotics))

exclude_meds = update(model, recompile = TRUE, cores = 4, newdata= diary %>% filter(reasons_for_exclusion == "") %>% filter(medication_psychopharmacological == 0, medication_hormonal == 0, medication_antibiotics == 0), file=paste0("brms_fits/", model_prefix, "rob_check_meds"))

summary(exclude_meds)
```

#### Excluding hypothesis guessers

```{r}
hyp_guess = update(model, recompile = TRUE, cores = 4,newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(hypothesis_guess_topic == "no_guess"), file=paste0("brms_fits/", model_prefix, "_rob_check_hyp_guess"))

summary(hyp_guess)
```

#### Excluding women using awareness-based methods

```{r}
unaware = update(model, recompile = TRUE, cores = 4,newdata = diary %>% filter(reasons_for_exclusion == "") %>% filter(contraception_approach != "awareness", contraception_app == 0), file=paste0("brms_fits/", model_prefix, "rob_check_unaware"))

summary(unaware)
```

#### Don't adjust for menstruation

```{r}
dont_adjust = update.formula(formula(model), new = . ~ . - menstruation*hormonal_contraception - premenstrual_phase_fab*hormonal_contraception + hormonal_contraception)
no_mens = update(model, recompile = TRUE, cores = 4, formula = dont_adjust, file=paste0("brms_fits/", model_prefix, "rob_check_no_mens2"))


summary(no_mens)
```

#### Don't adjust for menstruation interaction (bad pre-reg model)
We originally preregistered a model, in which we did not fit an interaction
between hormonal contraception and (pre-)menstruation. However, if we want to adjust the effect of the probability of being in the fertile window for (pre-)menstruation, we need to include "interaction controls". This robustness check shows that this decision makes little difference to the results.

```{r}
dont_adjust = update.formula(formula(model), new = . ~ . - menstruation:hormonal_contraception - premenstrual_phase_fab:hormonal_contraception)
no_mens_int = update(model, recompile = TRUE, cores = 4, newdata = diary %>% filter(reasons_for_exclusion == ""), formula = dont_adjust, file=paste0("brms_fits/", model_prefix, "rob_check_no_mens_int"))

summary(no_mens_int)
```

#### Using forward counting

```{r}
forward_counted = update(model, 
                         recompile = TRUE, cores = 4,
                         newdata = diary %>% 
                           filter(reasons_for_exclusion == "fertility_never_estimable, next_menstrual_onset_unobserved, " | reasons_for_exclusion == "next_menstrual_onset_unobserved, " | reasons_for_exclusion == "") %>% 
                           mutate(fertile_fab = prc_stirn_b_forward_counted, premenstrual_phase_fab = premenstrual_phase_forward_counted),
                         file=paste0("brms_fits/", model_prefix, "rob_check_forward_counted2"))

summary(forward_counted)
```

#### Using forward counted narrow window

```{r}
forward_counted_window = update(model, 
                         recompile = TRUE, cores = 4,
                         newdata = diary %>% 
                           filter(reasons_for_exclusion == "fertility_never_estimable, next_menstrual_onset_unobserved, " | reasons_for_exclusion == "next_menstrual_onset_unobserved, " | reasons_for_exclusion == "") %>% 
                           mutate(fertile_fab = fertile_narrow_forward_counted), 
                         formula = . ~ . - (premenstrual_phase_fab + menstruation) * hormonal_contraception,
                         file = paste0("brms_fits/", model_prefix, "rob_check_forward_counted_window"))

summary(forward_counted_window)
```


#### Using backward counted narrow window

```{r}
backward_counted_window = update(model, 
                         recompile = TRUE, cores = 4,
                         newdata = diary %>% 
                           filter(reasons_for_exclusion == "") %>% 
                           mutate(fertile_fab = fertile_narrow), 
                         formula = . ~ . - (premenstrual_phase_fab + menstruation) * hormonal_contraception,
                         file = paste0("brms_fits/", model_prefix, "rob_check_backward_counted_window"))

summary(backward_counted_window)
```

#### Using backward-counting squished

```{r}
bc_squished = update(model, recompile = TRUE, cores = 4,newdata = diary %>% filter(reasons_for_exclusion == "") %>% mutate(fertile_fab = prc_stirn_b_squished, premenstrual_phase_fab = premenstrual_phase_squished), file=paste0("brms_fits/", model_prefix, "rob_check_bc_squished"))

summary(bc_squished)
```

#### Using inferred backward-counting

```{r}
bc_inferred = update(model, recompile = TRUE, cores = 4,newdata = diary  %>% filter(reasons_for_exclusion == "fertility_never_estimable, next_menstrual_onset_unobserved, " | reasons_for_exclusion == "next_menstrual_onset_unobserved, " | reasons_for_exclusion == "")  %>% mutate(fertile_fab = prc_stirn_b_inferred, premenstrual_phase_fab = premenstrual_phase_inferred), file=paste0("brms_fits/", model_prefix, "rob_check_bc_inferred"))

summary(bc_inferred)
```



#### Related men inferred
```{r mod_fam_inferred}
if(outcome == "person_is_related_man_seen") {
  related_men_inferred <- update(model, recompile = TRUE, formula = person_is_related_man_inferred_seen ~ ., newdata = diary %>% filter(reasons_for_exclusion == ""), file = paste0("brms_fits/", model_prefix, "related_men_inferred"))
  summary(related_men_inferred)
}
```


#### Related men thought about
```{r}
if(outcome == "person_is_related_man_seen") {
  related_men_thoughts <- update(model, recompile = TRUE, formula = person_is_related_man_thoughts ~ ., newdata = diary %>% filter(reasons_for_exclusion == ""),  file = paste0("brms_fits/", model_prefix, "related_men_thoughts"))
  summary(related_men_thoughts)
}
```

#### Related men seen/thought about
```{r}
if(outcome == "person_is_related_man_seen") {
  related_men <- update(model, recompile = TRUE, formula = person_is_related_man ~ ., newdata = diary %>% filter(reasons_for_exclusion == ""),  file = paste0("brms_fits/", model_prefix, "related_men"))
  summary(related_men)
}
```


#### Summary plot {.active}

```{r fig.width=7,fig.height=7}
library(broom.mixed)
robchecks_e <- list(
  `A1. Original model` = model,
  `E1. No exclusions` = no_exclusions,
  `E2. No hypothesis guessing` = hyp_guess,
  `E3. No medication` = exclude_meds,
  `E4. No cycle-aware` = unaware,
  `E5a. No irregular cycles (>± 2 days)` = rob_check_menstruation_regularity,
  `E5b. Avg. cycles inside 25-35 days` = rob_check_selfrepcycle_length,
  `E5c. No cycles < 25 days` = rob_check_mens_length,
  `E5d. Low uncertainty about cycle (<±2 days)` = rob_check_menstruation_certainty,
  `E6. No planned pregnancy` = pregnant_trying,
  `E7. No unhealthy women` = rob_check_health,
  `E8a. Women 18-25` = younger25,
  `E8b. Women older than 25` = older25,
  `E9a. Friday-Saturday only` = weekend,
  `E9b. Monday-Thursday only` = weekday,
  `E10. Include living with parents` = rob_check_parents
  )
if(outcome != "person_is_related_man_seen") {
  robchecks_e[["E11. Singles only"]] = rob_check_singles 
}
robchecks_e <- robchecks_e %>%
  map(function(x) {
          b <- broom::tidy(x, conf.level = 0.99)
          b$n_days = nrow(x$data)
          b$n_persons = max(n_distinct(x$data$person),
                            n_distinct(x$data$short))
          b$category = "exclusions"
          b
          }) %>% 
  bind_rows(.id = "check")

robchecks_e %>% 
  filter(term == "fertile_fab") %>% 
  mutate(check = fct_rev(fct_inorder(paste0('atop("",atop("', check,'",',
                                'phantom(0)^"(',n_persons, ' women, ',n_days,' days)"))')))) %>% 
  ggplot(aes(check, estimate, ymin = conf.low, ymax = conf.high)) + 
  geom_hline(yintercept = 0, linetype = 'dashed') +
  scale_x_discrete("Robustness check", labels = function(x) {parse(text=x)}) +
  ylab("Fertile window effect with 99% CI") +
  geom_pointrange() + 
  coord_flip() +
  theme(axis.text.y = element_text(size = 11))
ggsave(paste0("figures/", model_prefix,"_robustness_checks_exclusions.png"), width =5, height = 7)
ggsave(paste0("figures/", model_prefix,"_robustness_checks_exclusions.pdf"), width =5, height = 7)

robchecks_p <- list(
  `A1. Original model` = model,
  `P1. Not adj. for (pre-)mens.` = no_mens,
  `P2. No HC×(pre-)mens. interaction` = no_mens_int,
  `P3. Forward counting` = forward_counted,
  `P4. Squished backward-counting` = bc_squished,
  `P5. Inferred backward-counting` = bc_inferred,
  `P6. Forward counted window` = forward_counted_window,
  `P7. Backward counted window` = backward_counted_window,
  `M1. Full random slopes` = full_random_slopes,
  `M2. Uncorrelated random slopes` = full_random_slopes_no_cor,
  `M3. No random slopes` = no_varying_slope,
  `M4. Require outcome variance` = with_outcome_var
  )

if(model$family$family == "gaussian") {
  robchecks_p[["M6. Ordinal regression"]] = ordinal_model 
} else {
  robchecks_p[["M5. Gaussian regression"]] = gaussian_model 
}

if(outcome == "person_is_related_man_seen") {
  robchecks_p[["O1. Inferred male relatives"]] = related_men_inferred
  robchecks_p[["O2. Related men thought about"]] = related_men_thoughts
  robchecks_p[["O3. Related men seen/thought about"]] = related_men
}

robchecks_p <- robchecks_p %>%
  map(function(x) {
          b <- broom::tidy(x, conf.level = 0.99)
          b$n_days = nrow(x$data)
          b$n_persons = max(n_distinct(x$data$person),
                            n_distinct(x$data$short))
          b$category = "model"
          b
          }) %>% 
  bind_rows(.id = "check")

robchecks_p %>% 
  filter(term == "fertile_fab") %>% 
  mutate(check = fct_rev(paste0('atop("",atop("', check,'",',
                                'phantom(0)^"(',n_persons, ' women, ',n_days,' days)"))'))) %>% 
  ggplot(aes(check, estimate, ymin = conf.low, ymax = conf.high)) + 
  geom_hline(yintercept = 0, linetype = 'dashed') +
  scale_x_discrete("Robustness check", labels = function(x) {parse(text=x)}) +
  ylab("Fertile window effect with 99% CI") +
  geom_pointrange() + 
  coord_flip() +
  theme(axis.text.y = element_text(size = 11))
ggsave(paste0("figures/", model_prefix,"_robustness_checks_model.png"), width =5, height = 7)
ggsave(paste0("figures/", model_prefix,"_robustness_checks_model.pdf"), width =5, height = 7)



bind_rows(robchecks_e, robchecks_p) %>% 
  filter(term == "fertile_fab") %>% 
  mutate(check = fct_rev(fct_inorder(paste0('atop("",atop("', check,'",',
                                'phantom(0)^"(',n_persons, ' women, ',n_days,' days)"))')))) %>% 
  ggplot(aes(check, estimate, ymin = conf.low, ymax = conf.high)) + 
  geom_hline(yintercept = 0, linetype = 'dashed') +
  scale_x_discrete("Robustness check", labels = function(x) {parse(text=x)}) +
  ylab("Fertile window effect with 99% CI") +
  geom_pointrange() + 
  coord_flip() +
  facet_wrap(~ category, scales = "free_y") + 
  theme(axis.text.y = element_text(size = 11),
        strip.text = element_blank())
ggsave(paste0("figures/", model_prefix,"_robustness_checks.png"), width = 7, height = 7)
ggsave(paste0("figures/", model_prefix,"_robustness_checks.pdf"), width = 7, height = 7)
```
