---
title: "Fertility and Kin"
output: html_document
---


# No evidence that inbreeding avoidance is up-regulated during the ovulatory phase of the menstrual cycle

This website documents analyses and results for Study 2 (Goettingen Ovulatory Cycle Diaries 2). It accompanies the supplement on [OSF](https://osf.io/f2hct/).

- [Helper functions](0_helpers.R)
- [Data subsetting and pre-processing](1_subset_data.html). More pre-processing is documented [here](https://rubenarslan.github.io/gocd2/).
- [Descriptive statistics](1_descriptives.html). More descriptive statistics and codebook [here](https://rubenarslan.github.io/gocd2/).
- [Main analyses](2_analyses_relatedness.html)
- [Robustness analyses](3_robustness_analyses.html)


### Reproducibility
This repository uses the [renv](https://rstudio.github.io/renv/) package to make
it easier to rerun analyses using the same setup and package versions that were
used to create them.

<details><summary>Here's a classical session info.</summary>

```{r}
library(codebook)
library(tidylog)
library(effsize)
library(effects); library(lme4); library(lmerTest); library(knitr); library(brms)
library(sjPlot)
sessionInfo()
```

</details>

<details><summary>Here's our renv lockfile.</summary>

```{r}
cat(readLines("renv.lock"), sep = "\n")
```
</details>
